\article{Student Governance}
\section{Authority.}
    All authority under this Constitution is derived from the students of the University of Michigan.

\section{Governments}
    All central governance powers vested herein shall be vested in a Central Student Government. The Central Student Government shall be democratically constituted, and shall consist of central legislative, executive, and judicial offices in which shall be vested with powers listed below. All powers not listed herein shall devolve to the additional governments for each school or college, University-owned and operated housing (and for each individual house and building therein), fraternities, sororities, and cooperatives; and for such jurisdictions as the smallest government containing the jurisdiction shall certify. The creation, structure, functions, and operations of each government shall be determined by the government's student constituency.

    Each student government or organization, each housing unit, and each federation of student governments, organizations, or housing units shall have a constitution approved by the students within the jurisdiction of the government, organization, housing unit, or federation providing for the democratic selection of its leadership and representative and democratic policy making within the government, organization, housing unit, or federation. Each such democratically constituted government shall be the governmental representative, legislative, and coordinating organization of the students of that jurisdiction, shall, upon a majority vote of its student constituents levy dues, and provide for their collection equally from each of the student constituents of the government; shall appropriate its own dues money and such other income as it shall receive; shall make appointments of student representatives to all student seats on committees whose purview is coextensive with the jurisdiction containing that committee; and shall conduct its elections so as to insure that its constituents are given ample opportunity to cast their ballots, that the election is free from fraud and that open campaigning can take place.
