\article{Student Rights}
\section{Freedom of Speech.}
    No authority, academic or civil, shall infringe upon a student's freedom of speech, freedom to publish, or freedom peaceably to assemble and demonstrate grievances.


\section{Freedom of Association.}
    Students shall have the right to form, join, and engage in organizations and associations; to use campus facilities for meetings and other activities, subject only to normal expenses when necessary and to such uniform regulations as may be required for scheduling and use purposes; and to, through such organizations and subject to such regulations, solicit money on campus.


\section{Fair Regulation.}
    Students shall be free from all rules and regulations not uniform in nature or not fully and clearly formulated, published, and made known to all students. No student shall be subject to any non-academic rule over which no democratic constituency to which that student belongs may amend.


\section{Democratic Representation.}
    Students shall have the right to form and maintain a democratic student government vested with the power to administer and regulate affairs primarily concerning students, to levy and collect dues, and to be represented in the formulation of University policy.


\section{Fair Housing Regulation.}
    Residents in University-owned, affiliated, or associated housing shall have the power to, democratically and subject to periodic review, regulate dress, conduct, and activities within their residence.


\section{Trial by Peers.}
    Students shall have the right to a fair and impartial hearing for all grievances under this Constitution or any regulation promulgated by the University before a judiciary of their peers.


\section{Privacy.}
    Students shall be free from unreasonable searches and seizures in their persons, possessions, and residences, and shall enjoy full access to and privacy of their academic, non-academic, and disciplinary records.


\section{Due Process.}
    Students shall enjoy the rights of due process before any University judiciary, to include the right to a speedy hearing, the right to confront accusers and witnesses, the right to competent counsel, a presumption of innocence in all disciplinary matters, freedom from cruel and unusual punishment, and the right to an appeal. No student shall be twice put in jeopardy for the same offense, or suspended or expelled except in cases of academic failure, failure to pay a University debt, or failure to abide by the safety and rights of other members of the University community.


\section{Petition.}
    Students shall enjoy the right to inquire into, and be honestly and fully informed regarding, any university policy, the process by which it was adopted, and the means by which it might be changed; and students shall be able to petition the University for redress of any policy.


\section{Equal Protection.}
    Students shall enjoy equal protection of laws and rules without regard to race, religion, gender, sexual orientation, age, marital status, disability, creed, or any other unreasonable consideration.